Viscous Transport in Eroding Porous Media

### 2019-06-13 docs/transport/erosion_transport.tex
do the result section in transport paper

In Fig.~\ref{fig:Eroding20tort} we release 1000 tracers 
from the starting cross section x = -1 to 
the end cross section x = 1 and 
use the local tortuosity to analysis the effect
of the geometrical structure on fluid velocity field. In
Fig.~\ref{fig:Eroding20tort}(a) the graph represents the ratio of the
x-component velocity u(-1, y) to its maximum velocity $u_{max}=6.2281
\times 10^{-4}$ at equal spreading tracers on the starting cross section.
The velocity is continuous along the starting cross section and
acting as several Poiseuille flows. This velocity graph is different
from the one in~\cite{matyka2008tortuosity} since we choose our cross
section to be the beginning of the flow before the fluid touches any
body. In Fig.~\ref{fig:Eroding20tort}(b) we record the local tortuosity
$\tau(y)=\lambda(y)/d$
of the tracers at $y$ on the starting cross section x = -1 
where $d = 2$.
This graph is not continuous
and the jumps in $\tau$ mean that the initial neighboring tracers have been
seperated by the bodies. 
}

@@

To study the behavior of fluid in the porous media with multiple bodies, 
we release 1000 equal spreeding tracers from the 
starting cross section x = -1 and record their trajectories and velocities
until they arrive the end cross section x = 1. 
To understand the global action of fluid qualitatively, 
we only draw 200 historical trajectories from x = -1 to x = 1 
in Fig.~\ref{fig:Eroding100tracer}.

To measure the local behavior of fluid quantitatively, 
we use the velocities and local tortuosities at the starting cross section 
to analysis the interaction of fluid and bodies until the end cross section 
in Fig.~\ref{fig:Eroding100tort}.
In Fig.~\ref{fig:Eroding100tort}(a) the graph represents the ratio of the
x-component velocity u(-1, y) to its maximum velocity $u_{max}=3.9021
\times 10^{-4}$ at equal spreading tracers on the strating cross section.

>>>>

In Fig.~\ref{fig:Eroding20tort} we release 1000 tracers 
from the starting cross section x = -1 to 
the end cross section x = 1 and 
use the local tortuosity to analysis the effect
of the geometrical structure on fluid velocity field when the porosity is 62.9 \%.
In Fig.~\ref{fig:Eroding20tort}(a) the graph represents the ratio of the
x-component velocity u(-1, y) to its maximum velocity $u_{max}=6.2281
\times 10^{-4}$ at equal spreading tracers on the starting cross section.
The velocity is continuous along the starting cross section and
acting as several Poiseuille flows. This velocity graph is different
from the one in~\cite{matyka2008tortuosity} since we choose our cross
section to be the beginning of the flow before the fluid touches any
body. In Fig.~\ref{fig:Eroding20tort}(b) we record the local tortuosity
$\tau(y)=\lambda(y)/d$
of the tracers at $y$ on the starting cross section x = -1 
where $d = 2$.
This graph is not continuous
and the jumps in $\tau$ mean that the initial neighboring tracers have been
seperated by the bodies. 
}

@@

To study the behavior of fluid in the porous media with multiple bodies, 
we release 1000 equal spreeding tracers from the 
starting cross section x = -1 and record their trajectories and velocities
until they arrive the end cross section x = 1 
and the porosity of this geometric structure is 62.98 \%. 
To understand the global action of fluid qualitatively, 
we only draw 200 historical trajectories from x = -1 to x = 1 
in Fig.~\ref{fig:Eroding100tracer}.

To measure the local behavior of fluid quantitatively, 
we use the velocities and local tortuosities at the starting cross section 
to analysis the interaction of fluid and bodies until the end cross section 
in Fig.~\ref{fig:Eroding100tort}.
In Fig.~\ref{fig:Eroding100tort}(a) the graph represents the ratio of the
x-component velocity u(-1, y) to its maximum velocity $u_{max}=3.9021
\times 10^{-4}$ at equal spreading tracers on the strating cross section.
As in the case of 20 nearly touching bodies, the velocity is continuous along
the starting cross section and acting as a Poiseuille flow in the channel between
bodies. But the velocity of the fluid with 100 bodies on the starting cross section 
changes more rapidly than the velocity of the fluid with 20 bodies 
and the local maximum velocity of the fluid with 100 bodies 
on the starting cross section is higher than the maximum velocity 
of the fluid with 20 bodies. The reason of the rapid change and 
high velocity on the starting cross section of 100-body case is because there are 
more bodies near the starting cross section in
100-body case than in the 20-body case. So the inlet flow in 100-body case
will be separated into more branches than the flow in 20-body case. 
Furthermore, under the fixed pressure drop condition the speed of flow in a channel is faster 
when the channel is smaller.
